---
title: "Analysis_LoL"
author: "Marshall Gallt"
date: "2/28/2022"
output: github_document
---



# Introduction

League of Legends is a popular PC game. Teams all around the world compete with
the hopes of making it to Worlds. Riot has released data for each player of each
professional game of the 2022 season thus far. In this project I will perform 
logistic regression in R on 
`2022_LoL_esports_match_data_from_OraclesElixir_20220228.csv`.


# Research Questions

In this logistic regression a number of questions could be posed. Examples
include, what indicates a winning score for each role, when is gold income the
most important, what objectives are the most decisive, how do the teams and
leagues differentiate in strategy.

# Data
The data we have available is:

Variable | Type | Description
---------|------|------------
gameid | Character | 
datacompleteness | Categorical | 
url | Character | 
league | Categorical | 
year | Date | 
split | Categorical |
playoffs | Binary |
date | Date |
game | Categorical |
patch | Categorical |
participantid | Numeric |
side | Categorical |
position | Categorical |
playername | Character | 
playerid | Character |
teamname | Character |
teamid | Character |
champion | Categorical |
ban1 | Categorical |
ban2 | Categorical |
ban3 | Categorical |
ban4 | Categorical |
ban5 | Categorical |
gamelength | Numeric |
result | Binary |
kills | Numeric |
deaths | Numeric |
assists | Numeric |
teamkills | Numeric |
teamdeaths | Numeric |
doublekills | Numeric |
triplekills | Numeric |
quadrakills | Numeric |
pentakills | Numeric |
firstblood | Numeric |
firstbloodkill | Numeric |
firstbloodassist | Numeric |
firstbloodvictim | Numeric |
team kpm | Numeric |
ckpm | Numeric |
firstdragon | Binary |
dragons | Numeric |
opp_dragons | Numeric |
elementaldrakes | Numeric |
opp_elementaldrakes | Numeric |
infernals | Numeric |
mountains | Numeric |
clouds | Numeric |
oceans | Numeric |
chemtechs | Numeric |
hextechs | Numeric |
dragons (type unkown) | Numeric |
elders | Numeric |
opp_elders | Numeric |
firstherald | Binary |
heralds | Numeric |
opp_heralds | Numeric |
firstbaron | Binary |
barons | Numeric |
opp_barons | Numeric |
firsttower | Binary |
towers | Numeric |
opp_towers | Numeric |
firstmidtower | Binary |
firsttothreetowers | Binary |
turretplates | Numeric |
opp_turretplates | Numeric |
inhibitors | Numeric |
opp_inhibitors | Numeric |
damagetochampions | Numeric |
dpm | Numeric |
damageshare | Numeric |
damagetakenperminute | Numeric |
damagemitigatedperminute | Numeric |
wardsplaced | Numeric |
wpm | Numeric |
wardskilled | Numeric |
wcpm | Numeric | 
controlwardsbought | Numeric |
visionscore | Numeric |
vspm | Numeric |
totalgold | Numeric |
earnedgold | Numeric |
earned gpm | Numeric |
earnedgoldshare | Numeric |
goldspend | Numeric |
gspd |
total cs | Numeric |
minionkills | Numeric |
monsterkills | Numeric |
monsterkillsownjungle | Numeric |
monsterkillsenemyjungle |  Numeric |
cspm | Numeric |
goldat10 | Numeric |
xpat10 | Numeric |
csat10 | Numeric |
opp_goldat10 | Numeric |
opp_xpat10 | Numeric |
opp_csat10 | Numeric |
golddiffat10 | Numeric |
xpdiffat10 | Numeric |
csdiffat10 | Numeric |
killsat10 | Numeric |
deathsat10 | Numeric |
opp_killsat10 | Numeric |
opp_assistsat10 | Numeric |
opp_deathsat10 | Numeric |
goldat15 | Numeric |
xpat15 | Numeric |
csat15 | Numeric |
opp_goldat15 | Numeric |
opp_xpat15 | Numeric |
opp_csat15 | Numeric |
golddiffat15 | Numeric |
xpdiffat15 | Numeric |
csdiffat15 | Numeric |
killsat15 | Numeric |
assistsat15 | Numeric |
deathsat15 | Numeric |
opp_killsat15 | Numeric |
opp_assistsat15 | Numeric |
opp_deathsat15 | Numeric |

# Exploratory Data Analysis

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
Lol_match_data_2022 <- read_csv("2022_LoL_esports_match_data_from_OraclesElixir_20220228.csv")
```


``` {r exploration}
names(Lol_match_data_2022)
head(Lol_match_data_2022)
summary(Lol_match_data_2022)
```
We will use `result` as our response variable as that indicates
whether it was a win or a lose. 

## Data Visualization

```{r data_visualization}

for(i in 0:123) {
  if(is.numeric(x)) {
    hist(Lol_match_data_2022[,i], main = names(Lol_match_data_2022) [i])
  }
}

```

# Data Cleaning


# Data Analysis

# Hypotheses

# Modeling

# Conclusion




