---
title: "Analysis_LoL"
author: "Marshall Gallt"
date: "2/28/2022"
output: github_document
---

# Introduction

In this project I wish to explore possible indicators of a winning strategy. This will be observed as a whole and as groups by leagues, teams, and players. I then wish to use these indicators to compare teams and hypothesis the best team.

# Research Questions


# Data


# Exploratory Data Analysis




# Data Cleaning


# Data Analysis

# Hypotheses

# Modeling

# Conclusion



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
Lol_match_data_2022 <- read_csv("2022_LoL_esports_match_data_from_OraclesElixir_20220228.csv")

```
In this project I will be working with the `2022_LoL_esports_match_data_from_OraclesElixir_20220228` data provided by RIOT. The first thing needed to do is understand the way our data is constructed. I will do this by displaying a tibble of the data and a simple summary.


```{r Lol}
Lol_match_data_2022
summary(Lol_match_data_2022)
```
WThe very first thing i wish do to is compare some of the variables to `outcome` 

```{r outcome}
Lol_match_data_2022 %>%
  group_by(result) %>%
  filter(position == "sup") %>%
  summarise(total = n(),
            avgkills = mean(kills),
            avgdeaths = mean(deaths),
            avgassists = mean(assists))

Lol_match_data_2022 %>%
  ggplot(aes(kills, deaths, color = result, shape = position)) +
    geom_jitter(alpha = 0.05)

Lol_match_data_2022 %>%
  group_by(result) %>%
  filter(position == "jng") %>%
  summarise(total = n(),
            avgkills = mean(kills),
            avgdeaths = mean(deaths),
            avgassists = mean(assists))
Lol_match_data_2022 %>%
  group_by(result) %>%
  filter(position == "top") %>%
  summarise(total = n(),
            avgkills = mean(kills),
            avgdeaths = mean(deaths),
            avgassists = mean(assists))
Lol_match_data_2022 %>%
  group_by(result) %>%
  filter(position == "mid") %>%
  summarise(total = n(),
            avgkills = mean(kills),
            avgdeaths = mean(deaths),
            avgassists = mean(assists))
Lol_match_data_2022 %>%
  group_by(result) %>%
  filter(position == "bot") %>%
  summarise(total = n(),
            avgkills = mean(kills),
            avgdeaths = mean(deaths),
            avgassists = mean(assists))
            

```