---
title: "Analysis_LoL"
author: "Marshall Gallt"
date: "2/28/2022"
output: github_document
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lubridate)
Lol_match_data_2022 <- read_csv("2022_LoL_esports_match_data_from_OraclesElixir_20220228.csv")
```


# Introduction

League of Legends is a popular PC game. Teams all around the world compete with
the hopes of making it to Worlds. Riot has released data for each player of each
professional game of the 2022 season thus far. In this project I will perform 
logistic regression in R on the `2022 Match Data` found on Oracle Elixir's [downloads page](https://oracleselixir.com/tools/downloads).
`2022_LoL_esports_match_data_from_OraclesElixir_20220228.csv`


# Research Questions

In this logistic regression a number of questions could be posed. Examples
include, what indicates a winning score for each role, when is gold income the
most important, what objectives are the most decisive, how do the teams and
leagues differentiate in strategy.

# Data
The data we have available is quite large and detailed. So I will be reducing 
the data to key variables and LCS matches.

```{r reduce}
Lol_match_data_2022

LCS_matches <- Lol_match_data_2022 %>%
  filter(league == "LCS",
         position == "team") %>%
  subset(select = c('gameid',
                    'side',
                    'gamelength',
                    'result',
                    'firstblood',
                    'team kpm',
                    'firstdragon',
                    'dragons',
                    'firstbaron',
                    'barons',
                    'firsttower',
                    'towers',
                    'firstmidtower',
                    'firsttothreetowers',
                    'inhibitors',
                    'vspm',
                    'earned gpm',
                    'cspm'))

LCS_matches


```

Variable | Type | Description
---------|------|------------
gameid | Character | 
side | Categorical |
gamelength | Numeric |
result | Binary |
team kpm | Numeric |
firstdragon | Binary |
firstbaron | Binary |
barons | Numeric |
firsttower | Binary |
towers | Numeric |
firstmidtower | Binary |
firsttothreetowers | Binary |
inhibitors | Numeric |
vspm | Numeric |
earned gpm | Numeric |
cspm | Numeric |


# Exploratory Data Analysis

First, we conduct an exploratory data analysis.




## Numerical Summaries

```{r summary}
summary(LCS_matches)
```
From the a quick summary of our variables two things immediately stick out,
there are thousands of observations with missing values, and the numeric
variables have extreme values significantly deviant from the innerquartile
range.

This extreme variance is because our data observes the individual players of
each team as well as the team's combined values, r=ecognizable by 
`position == "team"`. 

## Graphical Summaries

### 

```{r summary-tables-1, warning=FALSE}

LCS_matches %>%
  group_by(result)%>%
  summarise()

  
```

# Data Cleaning



# Data Analysis



# Hypotheses



# Modeling



# Conclusion




